\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{lipsum}

\title{An Overview of Artificial Intelligence (AI)}
\author{Bara Al-Sedih}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
Artificial Intelligence (AI) is the simulation of human intelligence in machines programmed to think, learn, and make decisions. This paper provides a concise definition of AI, examples of its applications, and discusses its transformative potential across industries.
\end{abstract}

\section{Introduction}
Artificial intelligence (AI) encompasses the development of systems capable of performing tasks that typically require human intelligence, such as reasoning, learning, and problem-solving. With advances in computational power and algorithms, AI has transitioned from theoretical constructs to practical tools that shape our daily lives. This paper aims to define AI, highlight key examples, and briefly discuss its significance.

\section{Examples of AI Applications}
AI is omnipresent in modern technology. Common examples include:
\begin{itemize}
    \item \textbf{Virtual Assistants:} Tools like Siri, Alexa, and Google Assistant take advantage of natural language processing to interact with users.
    \item \textbf{Autonomous Vehicles:} Self-driving cars utilize computer vision and machine learning to navigate the roads and ensure safety.
    \item \textbf{Healthcare:} AI-driven diagnostics and predictive analytics help identify diseases and personalize treatment plans.
    \item \textbf{Finance:} Fraud detection systems and algorithmic trading rely on machine learning models.
\end{itemize}

\section{Conclusion}
Artificial Intelligence is a cornerstone of modern innovation, enabling machines to emulate cognitive processes. Its diverse applications, ranging from virtual assistants to life-saving healthcare solutions, illustrate its profound impact. As AI continues to evolve, it promises to unlock new opportunities and address complex global challenges, reshaping the future of humanity.

\end{document}
